Modeling defoliation of Pinus Radiata trees using hyperspectral remote sensing data

### 2018-07-31 01_writing/Schratz_hyperspectral.tex
add title
- add table with most imp variables - results: var imp

	\title{title}

@@

%To account for geometric offsets, we calculated every index five times using a buffer from 1 - 5 meter around the centroid of the respective tree.
To account for geometric offsets, we used a buffer of two meters around the centroid of the respective tree.
The mean value of all pixels touched by the buffer was assigned as the final value for each index.
Missing values were removed from the mean value calculation.
In total, 7875 Normalized Ratio Indices NRI have been calculated ($\frac{125*126}{2}$).
Due to four corrupted bands and some other numerical problems, few indices returned \texttt{NA} values for some observations.
These indices were removed from the dataset, leaving a total of 7471 variables without missing values.

@@

To find indices that contributed most to model performance, we used permutation-based variable importance on the best performing algorithm.

@@

% rmse vs defol and point dens
\begin{figure} [b!]
	\begin{center}
		\makebox[\textwidth]{\includegraphics[width=\textwidth] {../03_figures/results/plot-characteristics.pdf}}
		\caption{RMSE vs. mean point density, coefficient of variation and coefficient of variation / skewness.}
		\label{fig:plot-characteristics}
	\end{center}
\end{figure}

\subsubsection{Variable importance}

\ac{NRI}s using bands in the wavelength range of 770 nm - 820 nm (band 80 - band 89), which belongs to the infrared region, appear most often among the ten highest coefficient estimates across all plots (\autoref{tab:variable-importance}).
Only one vegeation index (Datt3) showed up among the most important predictors (Laukiz 1).
Luiando and Oiartzun also prefered bands with longer (938.39 nm (band 114) - 996.31 nm (band 126)) and shorter wavelengths (480.30 nm (band 18) - 503.26 (band 23)).
The first range again belongs to the infrared region while the second is within the region of the visible light, transitioning from blue to green.

% band importance
\begin{figure} [b!]
	\begin{center}
		\makebox[\textwidth]{\includegraphics[angle=90, height = 0.95\textheight] {../03_figures/results/important-bands_boxplot.pdf}}
		\caption{test}
		\label{fig:important-bands}
	\end{center}
\end{figure}

@@

The exact number of contributing pixels to the final index value of an observations cannot be determined as it depends on the location of the tree within the pixel grid.
If a tree is located at the border of a pixel, a buffer of e.g. three meters will include more pixels than if the point is located at the center of a pixel.
Also, if a tree is located at the border of the plot, some directions of the buffer will not contain image values.

>>>>

	\title{Modeling defoliation of Pinus Radiata trees using hyperspectral remote sensing data}

@@

To account for geometric offsets, we used a buffer of two meters around the centroid of the respective tree.
The mean value of all pixels touched by the buffer was assigned as the final value for each index.
Missing values were removed from the mean value calculation.
In total, 7875 Normalized Ratio Indices NRI have been calculated ($\frac{125*126}{2}$).
Due to four corrupted bands and some other numerical problems, few indices returned \texttt{NA} values for some observations.
These indices were removed from the dataset, leaving a total of 7471 variables without missing values.

@@

To find indices that contributed most to model performance, we used the internal variable importance measure of the \textit{xgboost} algorithm.
The score is calculated by taking the contribution of each feature for each tree in the fitted model.
The higher the score of a variable, the more important it is for the fitted model when making predictions \citep{chenXGBoostScalableTree2016}.

@@

% rmse vs defol and point dens
\begin{figure} [b!]
	\begin{center}
		\makebox[\textwidth]{\includegraphics[width=\textwidth] {plot-characteristics.pdf}}
		\caption{RMSE vs. mean point density, coefficient of variation and coefficient of variation / skewness.}
		\label{fig:plot-characteristics}
	\end{center}
\end{figure}

Variable

The 7 most important features are vegetation indices with \textit{EVI} \citep{hueteComparisonVegetationIndices1997} being the most important one.

\begin{equation}
	EVI = 2.5*\frac{R_{800}-R_{670}}{R_{800}-(6*R_{670})-(7.5*R_{475})+1)}
\end{equation}

Vegetation index \textit{GDVI} appears three times among the first seven features.
This is because the \textit{hsdar} package computes the index four times, with \texttt{n} ranging from 1-4 \citep{wuEstimatingChlorophyllContent2008}:

\begin{equation}
	GDVI = \frac{R_{800}^n-R_{680}^n}{R_{800}^n+R_{680}^n}
\end{equation}

The first seven features (\textit{EVI}, \textit{GDVI4}, \textit{D1}, \textit{GDVI3}, \textit{GDVI2}, \textit{mNDVI} and \textit{mSR}) show a substantial difference compared to all following variables.

\begin{figure} [b!]
	\begin{center}
		\makebox[\textwidth]{\includegraphics[angle=90, height = 0.95\textheight] {var-imp-xgboost.pdf}}
		\caption{The 30 most important variables as estimated by the internal variable importance measure of the \textit{xgboost} algorithm. The higher the score, the more important the feature.
			"bf2" means that a buffer of 2 meter was used to extract the variable information to the tree observation. The following pattern describes the index: "NRI" means that a normalized ratio index with the following bands was used. Features without "NBI" are vegetation indices, e.g. "bf2\_EVI"}. %An overview of the vegetation indices can be found \href{https://rdrr.io/cran/hsdar/man/vegindex.html}{here}.}
		\label{fig:var-imp}
	\end{center}
\end{figure}

\begin{table}[t!]
\centering
\caption[t]{Formulas of the five most important vegetation indices of the super model. $R$ = Reflectance at wavelength, $D$ = First derivation of reflectance value at wavelength.}
\begingroup\footnotesize
\begin{tabular}{llll}
	\\
	Acronym & Name                                    & Formula                                                                 & Reference                                   \\
	\hline
	EVI     & Enhanced vegetation index               & $2.5*\frac{R_{800}-R_{670}}{R_{800}-(6*R_{670})-(7.5*R_{475})+1)}$        & \cite{hueteComparisonVegetationIndices1997}                                       \\
	GDVI    & Generalized DVI* & $\frac{R_{800}^n-R_{680}^n}{R_{800}^n+R_{680}^n}$                       & \cite{wuEstimatingChlorophyllContent2008}  \\
	D1      &         Derivative Index                                & $\frac{D_{730}}{D_{706}}$                                                       & \cite{zarco-tejadaSteadystateChlorophyllFluorescence2003} \\
	mNDVI   & Normalized DVI*  & $  \frac{R_{800}-R_{680}}{(R_{800}+R_{680}-2*R_{445}}$                       & \cite{simsRelationshipsLeafPigment2002}    \\
	mSR     & Simple Ratio Index                      & $\frac{R_{800}-R_{445}}{R_{680}-R_{445}}$                                   & \cite{simsRelationshipsLeafPigment2002}    \\
	\bottomrule
	\multicolumn{2}{l}{\small{* Difference Vegetation Index}}
\end{tabular}
\endgroup
\label{tab:supermodel_performance}
\end{table}

@@

The exact number of contributing pixels to the final index value of an observation cannot be determined as it depends on the location of the tree within the pixel grid.
If a tree is located at the border of a pixel, a buffer of e.g. three meters will include more pixels than if the point is located at the center of a pixel.
Also, if a tree is located at the border of the plot, some directions of the buffer will not contain image values.
